Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-12-23 paper/preprint/appendix.Rmd
add appendix code for rendering examples / new figure

```{r}
prf_by_age_faces <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$face_eval_ketan)) %>%
  filter(num_detect > 50)

prf_by_age_hands <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$hand_eval_ketan)) %>%
  filter(num_detect > 50)
```

```{r, fig.width=6.5, fig.height=3.2}

@@

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')

ggarrange(p1, p2, nrow=1)

# p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Precision - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# 
# p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Recall - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# #
# ggarrange(p1,p2,p3)

@@

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos.}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location.}
# single location videos
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
```

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos).}
# normalize by location
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
  group_by(Activity, Location) %>%
  summarise(n = n(),
            prop_loc = n / loc_freq) %>% 
  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

```{r}
prf_by_age_faces <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$face_eval_ketan))

prf_by_age_hands <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$hand_eval_ketan)) 
```

```{r, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}

@@

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')
```

```{r}
ggarrange(p1, p2, nrow=1)
```

```{r}
# p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Precision - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# 
# p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Recall - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# #
# ggarrange(p1,p2,p3)

@@

# OpenPose Annotation Examples
```{r include=FALSE}
load(file = here::here('data/preprocessed_data_2021/goldset_category_annotations.RData'))

fp_face_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FP')

fp_hand_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(hand_eval_ketan == 'FP')

fn_face_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FN')

fn_hand_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FN')

images_to_render =  fp_hand_examples
which_images = 'fp_hand_examples'

public_urls = unique(images_to_render$public_url)
img_names_short = unique(images_to_render$img_name)

dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
  }

```{r}
det_types = c('FP','FN')

render_examples = FALSE
if (render_examples == TRUE) {
for (det_type in det_types) {
  to_render_hands <- d %>%
    distinct(vid_name, frame, public_url) %>%
    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
    filter(hand_eval_ketan == det_type) %>%
    ungroup() %>%
    dplyr::sample_n(7)

  image_read(to_render_hands$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))

  ###
    to_render_faces <- d %>%
    distinct(vid_name, frame, public_url) %>%
    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
    filter(face_eval_ketan == det_type) %>%
    ungroup() %>%
    dplyr::sample_n(7)

  image_read(to_render_faces$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))

}
}

```{r error_examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=6, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example false alarms/misses for faces/hands randomly sampled from the larger set of manual annotations."}
error_examples <- png::readPNG("figs/OP_errors.png")
grid::grid.raster(error_examples)
```

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location in videos taking place in only a single location."}
# single location videos
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("activity_by_location.pdf", width=6.5, height=3.5)
```

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
# normalize by location
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
  group_by(Activity, Location) %>%
  summarise(n = n(),
            prop_loc = n / loc_freq) %>% 
  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
